The Noisy Work of Uncertainty Visualisation Research: A Review

### 2024-07-26 paper.qmd
meeting update

```{r}
#| echo: false
#| message: false
#| warning: false
#| eval: false
#| label: fig-bivariate2
#| fig-cap: "A bivariate map that depict the counties of Iowa where each county is coloured acording to it's average daily temperature and the variance in temperature. This map is a variation on the previous bivariate map where instead of variance being mapped to colour saturation, it is mapped to colour value. Even though colour value is intergrable with colour hue, and colour value is naturally accociated with uncertainty, the spatial trend is still visible in the map."
#| fig-subcap: 
#|   - "High Variance Data"
#|   - "Low Variance Data"
#|   - "Bivariate Palette"
#| layout-ncol: 3
#| layout-valign: "bottom"

@@

# Bivariate maps 2
p2a1 <- my_map_data |>
  filter(variance_class=="lowvar") %>%
  ggplot() +
  geom_sf(aes(fill = biclass, geometry = geometry)) + 
  scale_fill_manual(values = bivariatepal2) +
  theme_void() + 
  theme(legend.position = "none")

@@

#p2a1
#p2b2
#show_pal2(colours = bivariatepal2, ncol=8, borders=NA, myxlab = "Temperature", myylab = "Variance", breaks = 21:29, breaks2 = 0:4)

>>>>

```{r}
#| echo: false
#| message: false
#| warning: false
#| eval: false
#| label: fig-bivariate2
#| layout-ncol: 3
#| layout-valign: "bottom"

#fig-cap: "A bivariate map that depict the counties of Iowa where each county is coloured acording to it's average daily temperature and the variance in temperature. This map is a variation on the previous bivariate map where instead of variance being mapped to colour saturation, it is mapped to colour value. Even though colour value is intergrable with colour hue, and colour value is naturally accociated with uncertainty, the spatial trend is still visible in the map."

@@

# Bivariate maps 2
p2a1 <- my_map_data |>
  filter(variance_class=="lowvar") %>%
  ggplot() +
  geom_sf(aes(fill = biclass, geometry = geometry), colour=NA) + 
  scale_fill_manual(values = bivariatepal2) +
  theme_void() + 
  theme(legend.position = "none")

@@

p2a1
p2b2
#show_pal2(colours = bivariatepal2, ncol=8, borders=NA, myxlab = "Temperature", myylab = "Variance", breaks = 21:29, breaks2 = 0:4)
